|

### 2020-05-12 README.Rmd
spell check for CRAN, rename functions

```{r echo = FALSE, results = "asis"}
descripts <- data.frame(matrix(c(
  "_pkgdown.yml", "YAML for package website", "do not edit",
  "DESCRIPTION", "R-package DESCRIPTION", "do not edit",
  "LICENSE.md", "Project license", "do not edit",
  "NAMESPACE", "R-package namespace", "machine-written",
  "README.md", "Read this file to get started! ", "do not edit",
  "README.Rmd", "R-markdown source for readme.md", "human editable",
  "worcs.Rproj", "Rstudio project file", "do not edit",
  "docs/", "Package website", "machine-written",
  "inst/", "Rstudio project template files ", "human editable",
  "man/", "R-package documentation", "do not edit",
  "paper/", "WORCS paper source files", "human editable",
  "R/", "R-package source code", "human editable",
  "vignettes/", "R-package vignettes", "human editable"
), ncol = 3, byrow = TRUE))
names(descripts) <- c("File", "Description", "Usage")
knitr::kable(descripts)
```

@@

``` r
install.packages("devtools")
devtools::install_github("crsh/papaja", dependencies = TRUE)
devtools::install_github("cjvanlissa/worcs", dependencies = TRUE)
tinytex::install_tinytex()
worcs::git_credentials("your_name", "your_email")
```

>>>>

```{r echo = FALSE, results = "asis"}
descripts <- data.frame(matrix(c(
  "_pkgdown.yml", "YAML for package website", "do not edit",
  "DESCRIPTION", "R-package DESCRIPTION", "do not edit",
  "LICENSE.md", "Project license", "do not edit",
  "NAMESPACE", "R-package namespace", "machine-written",
  "README.md", "Read this file to get started! ", "do not edit",
  "README.Rmd", "R-markdown source for readme.md", "human editable",
  "worcs.Rproj", "RStudio project file", "do not edit",
  "docs/", "Package website", "machine-written",
  "inst/", "RStudio project template files ", "human editable",
  "man/", "R-package documentation", "do not edit",
  "paper/", "WORCS paper source files", "human editable",
  "R/", "R-package source code", "human editable",
  "vignettes/", "R-package vignettes", "human editable"
), ncol = 3, byrow = TRUE))
names(descripts) <- c("File", "Description", "Usage")
knitr::kable(descripts)
```

@@

``` r
if(!requireNamespace("remotes"))install.packages("remotes")
remotes::install_github("cjvanlissa/worcs", dependencies = TRUE, update = "never")
remotes::install_github("crsh/papaja", dependencies = TRUE, update = "never")
tinytex::install_tinytex()
worcs::git_user("your_name", "your_email")
```

### 2020-05-12 paper/notes.Rmd
spell check for CRAN, rename functions

It is worth mentioning the free, open-source reference manager Zotero, because it can be used as easily in conjunction with Rstudio as with Word; the plugin BetterBibTex can export continuously updated `.bib` files for citation in Rmarkdown. Finally, it is worth noting that, as of June 2019, Zotero automatically flags retracted papers in your database. This might stop discredited papers from unnecessarily muddling the literature.
<!--Retracted papers

@@

Sharing code is essential for computational reproducibility. The easiest way to share fully reproducible code is to work with an Rstudio project that is version controlled using Git, combined with the `renv` package to ensure all package dependencies are tracked. Such a project can be uploaded ("pushed") wholesale to a code repository, such as GitHub. Projects on GitHub can be publically accessible, so that other researchers can browse the code or copy ("clone") the entire project. It is also possible to make the project private until the manuscript is accepted, which has the benefit that one can show the entire evolution of the analyses from conception to publication.

>>>>

It is worth mentioning the free, open-source reference manager Zotero, because it can be used as easily in conjunction with RStudio as with Word; the plugin BetterBibTex can export continuously updated `.bib` files for citation in Rmarkdown. Finally, it is worth noting that, as of June 2019, Zotero automatically flags retracted papers in your database. This might stop discredited papers from unnecessarily muddling the literature.
<!--Retracted papers

@@

Sharing code is essential for computational reproducibility. The easiest way to share fully reproducible code is to work with an RStudio project that is version controlled using Git, combined with the `renv` package to ensure all package dependencies are tracked. Such a project can be uploaded ("pushed") wholesale to a code repository, such as GitHub. Projects on GitHub can be publically accessible, so that other researchers can browse the code or copy ("clone") the entire project. It is also possible to make the project private until the manuscript is accepted, which has the benefit that one can show the entire evolution of the analyses from conception to publication.
